---
  title: "Homework 1"
---
  
---
title: "Quadratic Equations"
author: "Brooke Wills"
date: "February 14, 2017"
output: html_document
---

Below I define the quadratic equation in R using the funciton quad().

```{r }
quad <- function(x,a=0,b=0,c=0) {
  a*x^2+b*x+c
}
x <- seq(from=-10, to=10, by=.1)

a <- quad(x,a=3)
a2 <- quad(x,a=2)
a3 <- quad(x,a=1)
a4 <- quad(x,a=-1)
a5 <- quad(x,a=-2)

b <- quad(x,b=3)
b2 <- quad(x,b=2)
b3 <- quad(x,b=1)
b4 <- quad(x,b=-1)
b5 <- quad(x,b=-2)

c <- quad(x,c=3)
c2 <- quad(x,c=2)
c3 <- quad(x,c=1)
c4 <- quad(x,c=-1)
c5 <- quad(x,c=-2)

ab <- quad(x,a=3,b=1)
ab2 <- quad(x,a=2,b=-3)
ab3 <- quad(x,a=1,b=5)
ab4 <- quad(x,a=-1,b=2)
ab5 <- quad(x,a=-2,b=-5)

ac <- quad(x,a=3,c=1)
ac2 <- quad(x,a=2,c=-3)
ac3 <- quad(x,a=1,c=5)
ac4 <- quad(x,a=-1,c=2)
ac5 <- quad(x,a=-2,c=-5)

bc <- quad(x,b=3,c=1)
bc2 <- quad(x,b=2,c=-3)
bc3 <- quad(x,b=1,c=5)
bc4 <- quad(x,b=-1,c=2)
bc5 <- quad(x,b=-2,c=-5)
```

The plots below each show the effects of different values for the constants in the quadratic formula Ax^2+Bx+C and the other constants set to zero. When A is the only non zero number we get a curve with varying widths. When B is the only constant we see only lines at different angels and when C is the only constant we see horizontal lines paralell to the x axis. 

```{r, echo=FALSE}

plot(x,a,"l", main ="Different Values of A")
lines(x,a2)
lines(x,a3)
lines(x,a4)
lines(x,a5)

plot(x,b,"l", main ="Different Values of B")
lines(x,b2)
lines(x,b3)
lines(x,b4)
lines(x,b5)

plot(x,c,"l", main ="Different Values of C")
lines(x,c2)
lines(x,c3)
lines(x,c4)
lines(x,c5)

plot(x,ab,"l", main ="Different Values of A and B")
lines(x,ab2)
lines(x,ab3)
lines(x,ab4)
lines(x,ab5)

plot(x,ac,"l", main ="Different Values of A and C")
lines(x,ac2)
lines(x,ac3)
lines(x,ac4)
lines(x,ac5)

plot(x,bc,"l", main ="Different Values of B and C")
lines(x,bc2)
lines(x,bc3)
lines(x,bc4)
lines(x,bc5)
```

